Verifying Demonstrations

### 2019-10-16 paper/distance-bounding.tex
Changes DH title to also include DF, since it does
Minor clarification for comment
Fixes some typos

We will now define what is means for a protocol to be \ac{DBMF} resistant.

\begin{definition}[\acs*{DBMF} resistance~\cite{TREAD}]%
  \label{MFresistance}
  For \iac{DB} authentication scheme \(\DB\), a \((t, \qobs, \qp, \qv)\)-MF 
  adversary \(\adv\) \emph{wins} against \(\DB\) if the verifier accepts 
  \(\adv\) in in one of the \(\qv\) adversary--verifier sessions \(\sid\), 
  which does not have any critical phase tainted by a prover--adversary session 
  \(\sid'\).
  The protocol \(\DB\) is \Ac{DBMF} resistant if the probability 
  \(\Adv_{\DB}^{\text{MF}}(\adv)\) that \(\adv\) wins the game is negligible in 
  the security parameter.
\end{definition}

@@

\daniel{This definition differs slightly from that of 
  \textcite{FormalTerroristFraud}: we use \(m_{k'}\) instead of \(m_k'\).
  \Ie that the number of messages in \(\sid\) is not required to be the same 
  and in the same order as in \(\sid'\).}

@@

\paragraph*{\Acl*{DBDH}}

>>>>

We will now define what it means for a protocol to be \ac{DBMF} resistant.

\begin{definition}[\acs*{DBMF} resistance~\cite{TREAD}]%
  \label{MFresistance}
  For \iac{DB} authentication scheme \(\DB\), a \((t, \qobs, \qp, \qv)\)-MF 
  adversary \(\adv\) \emph{wins} against \(\DB\) if the verifier accepts 
  \(\adv\) in in one of the \(\qv\) adversary--verifier sessions \(\sid\), 
  which does not have any critical phase tainted by a prover--adversary session 
  \(\sid'\).
  The protocol \(\DB\) is \Ac{DBMF} resistant if the probability 
  \(\Adv_{\DB}^{\text{MF}}(\adv)\) that \(\adv\) wins is negligible in the 
  security parameter.
\end{definition}

@@

\daniel{The following definition differs slightly from that of 
  \textcite{FormalTerroristFraud}: we use \(m_{k'}\) instead of \(m_k'\).
  \Ie that the number of messages in \(\sid\) is not required to be the same 
  and in the same order as in \(\sid'\).}

@@

\paragraph*{\Acl*{DBDH} and \acl*{DBDF}}
